manuscript_notes

### 2024-12-10 notes/manuscript_notes.Rmd
update ms. and ms-notes
update ms. notes
add note
update ms. and ms-notes.

->

@@

-> cloglog-hazard is better I guess.

@@

->

@@

2. As (1) combine Figures 8 and 9.

->

@@

->

@@

->

@@

# Sven dec 8

I also moved prior predictive checks to last section of 2a.

Mention 2b ppc...

Section 4...

Tutorial 2a ... M1d...

>>>>

-> Done. Moved to tutorial only.

@@

-> cloglog-hazard is correct.

@@

-> Done. !!!!! delete one....

@@

2. As (1) combine Figures 8 and 9. (ames)

@@

-> Title removed before combining with Figure 7.

@@

-> AMEs was removed before combining with fig 8.

@@

# Sven dec 10

adjust small error in Figure 3 + check Figure 10 + add second panel to Figure 10

change ms code in section 4.1.2 (make it same as in tut)

Mention tut 2b priors...   todo

Section 4... comments?

appendices/separate Rmd file...

clean up html of Rmd files
